## The Spectra class
*Spectra* is the main S4 class provided by the package **geoSpectral**. It contains slots (members) that store the name of the spectral variable (**\@ShortName** and **\@LongName**), wavelengths of spectral data (**\@Wavelengths**), and units of wavelengths (**\@WavelengthsUnit**), spectral data (**\@Spectra**), non-spectral data (**\@data**), non-spectral data units (**\@Units**) metadata (**\@header**), spatial attributes (**\@sp**), temporal attributes (**\@time** and **\@endtime**) and class version (**\@ClassVersion**).

Let us examine the slots and their respective data types: 
```{r}
library('geoSpectral')
showClass("Spectra")
```
If you have a dataset that is non-spectral, you could use the *ST*, *STI* and *STIDF* classes provided by *spacetime* package that provides the slot **\@data**. This slot is optional in **geoSpectral**, but it makes it possible to work with non-spectral (ancillary) data as well.

## The SpcHeader class
All *Spectra* objects needs to contain a slot called **\@header**, an object of class **SpcHeader**. This class directly inherits the R *list* class. 
```{r}
showClass("SpcHeader")
```

All the regular methods that can be applied on an R *list* object can be applied to *SpcHeader* objects as well :
```{r}
h <- new("SpcHeader")
h
h$Station <- "21A"
h$Station
```

## The SpcList class
The *SpcList* is designed to store collections of several related **Spectra** objects together. Just like the *SpcHeader* class, the *SpcList* class as well inherits from R *list*:
